\thesistitle

### 2019-07-25 sections/introduction.tex
Addressing notes

\chapter{Introduction}
%\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
%Problem Analysis: Here you present your analysis of the problem situation that your research will address.
%How does this problem manifest itself at your host organisation?
%Also summarises existing scientific insight into the problem.}
\label{ch:introduction}
\todo{Rewrite this part}
Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality. There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}. However, most of these methods still require manual assessment of where and when to apply them. Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}. For a large part, refactoring requires domain knowledge to do it right. However, there are also refactoring opportunities that are rather trivial and repetitive to execute. In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve maintainability of the refactored code.

>>>>

\chapter{Introduction}
%\todo[inline,color=blue!10]{Context: what is the bigger scope of the problem you are trying to solve? Try to connect to societal/economical challenges.
%Problem Analysis: Here you present your analysis of the problem situation that your research will address.
%How does this problem manifest itself at your host organisation?
%Also summarises existing scientific insight into the problem.}
\label{ch:introduction}
Refactoring is used to improve quality related attributes of a codebase (maintainability, performance, etc.) without changing the functionality. There are many methods that have been introduced to help with the process of refactoring \cite{fowler2018refactoring, wake2004refactoring}. However, most of these methods still require manual assessment of where and when to apply them. Because of this, refactoring takes up a signification portion of the development process \cite{lientz1978characteristics, mens2004survey}, or does not happen at all \cite{mens2003refactoring}. For a large part, refactoring requires domain knowledge to do it right. However, there are also refactoring opportunities that are rather trivial and repetitive to execute. In this thesis, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve maintainability of the refactored code.
